---
output: github_document
---


# Algerian R Users Group live demo

In this demo, I tried to map the distribution of international tourists arrival per country in 2019. The video (in Algerian dialect) can be found [here](https://www.facebook.com/FaUx.DiLz.IHa/videos/3302395576438655/?comment_id=3060255194025475&notif_id=1586632143270686&notif_t=group_comment)



```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Loading the tidyverse package
```{r}

library(tidyverse)

```

## Extracting the data

```{r}
library(ralger)

data <-
  table_scrap("https://worldpopulationreview.com/countries/most-visited-countries/")

```

## Cleaning the columns' names
```{r}

data <- janitor::clean_names(data)

```


## Converting the character column to numeric
```{r}

data$international_tourist_arrivals <-
  parse_number(data$international_tourist_arrivals, na = "..")


```

## Getting the sf data

```{r }

library("rnaturalearth")
library("rnaturalearthdata")

world <- ne_countries(scale = "large", returnclass = "sf")


# The USA problem
world$sovereignt  <-
  world$sovereignt %>%  str_replace_all("United States of America", "United States")

  


```

## Joining the datasets

```{r}

final_data <-
  world %>% left_join(data, by = c("sovereignt" = "country"))


```

## Plotting the distribution of internation tourists around the world

```{r}


ggplot(final_data) +
  geom_sf(aes(fill = international_tourist_arrivals)) +
  scale_fill_gradientn(colours = c("darkred", "orange", "yellow",
                                   "lightblue", "steelblue", "blue")) +
  labs(fill = "Tourist Arrival",
       title = "Répartition du nombre de touristes par pays en 2019",
       caption = "Les pays en gris représentent des valeurs manquantes") +
  theme_dark()


```








